---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE, warnings=FALSE, message=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
devtools::load_all("~/Desktop/atacr")

```

# atacr

helps with the analysis of count data from RNA and ATAC capture-seq experiments.
    Using BioConductor RangedSummarizedExperiment objects, atacr implements a set of helper
    functions and quality control plots specific to the analysis of particularly windows.
    Especially, atacr is useful for performing control window based between sample normalizations and for
    easily running non-standard tests for differentially accessible windows in common reference designs.

## Installation

You can install atacr from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("TeamMacLean/atacr")
```



## Quick start:

```{r example, echo=TRUE, fig.height=7, fig.width=7}
library(atacr)
summary(sim_counts)
```

```{r}
plot(sim_counts)
```
