---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE, warnings=FALSE, message=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
devtools::load_all("~/Desktop/atacr")

```

# atacr

atacr helps with the analysis of count data from ATAC-seq experiments. Using BioConductor RangedSummarizedExperiment objects, atacr implements a set of helper functions and quality control plots specific to the analysis of particularly windows. Especially, atacr is useful for performing control window based normalisations and for easily running tests for differentially accessible windows in common reference designs with multiclass data.

## Installation

You can install atacr from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("TeamMacLean/atacr")
```



## Example

This is a basic example which shows you how to solve a common problem:

```{r example, echo=TRUE, fig.height=7, fig.width=7}
library(atacr)
summary(sim_counts)
```

```{r}
plot(sim_counts)
```
