---
title: "Summaries"
author: "Dan MacLean"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_caption: yes
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The `atacr` package provides functions for getting quick summaries of your data. An overview comes from `summary()`

```{r, echo=FALSE, eval=TRUE}
library(atacr)
counts <- simulate_counts()
```

```{r, echo=TRUE, eval=TRUE}
summary(counts)
```

which shows the on and off target hit counts, the quantiles and the mean read depths.

The count distributions across the bait and non-bait windows by sample can be plotted quickly with `coverage_summary()`.

```{r, echo=TRUE, eval=TRUE, fig.width=7}
coverage_summary(counts)
```

## Diagnostic plots 

It is possible to look coverage in a given data set and look at raw counts.

```{r, fig.width=7}
plot_counts(counts, which = "bait_windows", log10 = FALSE)
```

### Low counts in windows

The number of windows below a threshold for each experiment can be seen with `windows_below_coverage_threshold_plot()`, and you can set the lower and upper bounds with the `to` and `from` arguments.

```{r, echo=TRUE, eval=TRUE, fig.width=7}

windows_below_coverage_threshold_plot(counts, from = 5, to = 25)
```


### MA plots

MA plots of sample count versus all sample median count - to highlight odd looking experiments and extreme outliers - can be displayed with `ma_plot()`. By default this will use the `bait_windows` data, but you can set the `which` argument to use other subsets, e.g `non_bait_windows` 
```{r, fig.width=7}
ma_plot(counts)
```

### Per chromosome plots

These are bar charts of coverage at the windows across the chromosomes (`seqnames`) provided in the data.

```{r, fig.width=7, fig.height=7, fig.cap="The simulated data here are spread randomly across the chromosome."}
plot_count_by_chromosome(counts)
```

### Sample comparison plots

A matrix of correlation between counts in the samples can be plot with the `sample_correlation_plot()` function. In this plot the colour and size scale of the dots represents the Pearson correlation coefficient. Pairwise comparisons with _p_ < 0.05 have a blank space.

```{r, fig.width=7}
sample_correlation_plot(counts)
```

A PCA plot that clusters the most simlar samples can also be generated using the `sample_pca_plot()` function.  

```{r, fig.width=7}
sample_pca_plot(counts)
```
